### 2015-02-10 paper_40_mpi.tex
working on the quality element

\subsection{QUALITY}
    Measuring quality is a crucial part of accessing 
    software development results.  
    Poor quality means time, money, and resources are spent 
    fixing the problems. As a result, new features are not being
    created. One of the key indicators of software quality 
    is defects.  Thus, it is important
    to measure the number of defects associated with a software 
    release.  The following is an algorithm to calculate
    the quality score of software being released.

@@

        The development and testing effort can come from any of 
        the following choices for effort. 
        \begin{description}
            \item[Actual Time] This number is a representation of the 
                total amount of time spent on a project.  This number
                can be measured in any unit of time: hours, days, weeks,
                etc.  Actual time can be applied to development or testing
                effort.
            \item[Estimated Time] This number is a representation of the 
                initial estimated amount of time spent on a project.  This number
                can be measured in any unit of time: hours, days, weeks,
                etc.  Estimated time can be applied to development or testing
                effort.  It is common for the estimated and actual times
                to be diffent.
            \item[Source Lines Of Code (SLOC)]  This number is the count of 
                the total number of lines of source code for a project. 
                Obviously, 
                this item only counts as a level of
                effort for development unless coding in used to generate
                automated test cases. \footnote{Automated testing is the
                process of creating software to automatically run tests
                against other software.  The adoption of automated testing
                is varied and it is not a solution in all cases 
                \cite{Ramler2006}. }
            \item[Modified Lines Of Code] This number is a count of the number 
                of modified lines of source code. Modified lines is 
                defined as the number of deleted, added, and modified 
                lines of source code.  This number is different from above
                since it does not include all the lines of source code.  Similar
                to above, this number makes more sense for development effort.
            \item[Test Cases] A test case is a step or series of steps followed
                to validate some expected outcome of software.  Organizations
                will create a number of test cases to be validated for a
                software system.  The number of such test cases could
                be used as a level of testing effort.
        \end{description}

    \subsubsection{QUALITY FORMULA}
        The first step in creating a score for the quality
        element is analysis of the historical data.  The historical
        data is all quality data collected before  a given point
        in time.  Some common historical cutoffs are the current date
        or the end of the previous fiscal year.  Then a mathematical
        model to predict Defects in PROD will be produced.  In statistical
        terms, the response is \textit{Defects in PROD} and the predictors
        are: \textit{Defects in UAT}, \textit{Defects in SIT}, 
        \textit{Testing Effort}, and \textit{Development Effort}.

@@

Here is the problem for loading the data:
Given a data file with the above columns, can a regression model be automatically found
that fits the data?  The regression model will serve as the "target" for future 
releases.  Here is a list of possible things to automate to get a good model.
\begin{itemize}
\item Linear Regression
\item Stepwise Regression
\item Ridge Regression for suspected multicolinearity
\item Removal of outliers
\end{itemize}

>>>>

\subsection{QUALITY}
    Measuring quality is a crucial part of accessing 
    software development results.  
    Poor quality means time, money, and resources are spent 
    fixing the problems. As a result, new features are not being
    created. One of the key indicators of software quality 
    is defects.  Thus, it is important
    to measure the number of defects associated with a software 
    release.  The following is the necessary data to collect
    and an algorithm to calculate
    the quality score of software being released.

@@

        The development and testing effort can come from any of 
        the following choices for effort. It is possible
        that other measures will work for effort.
        \begin{description}
            \item[Actual Time] This number is a representation of the 
                total amount of time spent on a project.  This number
                can be measured in any unit of time: hours, days, weeks,
                etc.  Actual time can be applied to development or testing
                effort.
            \item[Estimated Time] This number is a representation of the 
                initial estimated amount of time spent on a project.  This number
                can be measured in any unit of time: hours, days, weeks,
                etc.  Estimated time can be applied to development or testing
                effort.  It is common for the estimated and actual times
                to be diffent.
            \item[Source Lines Of Code (SLOC)]  This number is the count of 
                the total number of lines of source code for a project. 
                Obviously, 
                this item only counts as a level of
                effort for development unless coding in used to generate
                automated test cases. \footnote{Automated testing is the
                process of creating software to automatically run tests
                against other software.  The adoption of automated testing
                is varied and it is not a solution in all cases 
                \cite{Ramler2006}. }
            \item[Modified Lines Of Code] This number is a count of the number 
                of modified lines of source code. Modified lines is 
                defined as the number of deleted, added, and modified 
                lines of source code.  This number is different from above
                since it does not include all the lines of source code.  Similar
                to above, this number makes more sense for development effort.
            \item[Test Cases] A test case is a step or series of steps followed
                to validate some expected outcome of software.  Organizations
                will create a number of test cases to be validated for a
                software system.  The number of such test cases could
                be used as a level of testing effort.
        \end{description}

    \subsubsection{QUALITY FORMULA}
        The first step in creating a score for the quality
        element is analysis of the historical data.  The historical
        data is all quality data collected before  a given point
        in time.  Some common historical cutoffs are the current date
        or the end of the previous fiscal year.  Then a mathematical
        model to predict Defects in PROD will be produced.  In statistical
        terms, the response is \textit{Defects in PROD} and the predictors
        are: \textit{Defects in UAT}, \textit{Defects in SIT}, 
        \textit{Testing Effort}, and \textit{Development Effort}.  
        Some of the following strategies will be employed to find 
        a reasonable model.
        \begin{itemize}
            \item Removal of outliers and/or influential points
            \item Linear Regression
            \item Stepwise Regression
            \item Ridge Regression for suspected multicolinearity
        \end{itemize}

        Once a model has been found, it will be labeled as $f$ and it
        will not change.  It serves as the quality baseline for MPI. 
        All future quality scores will be dependent upon the original
        $f$.

        After the model $f$ has been determined,

@@
